Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-08-15 alloscore_manuscript/manuscript.Rnw
Update alloscore_manuscript/manuscript.Rnw

The integrated allocation score (IAS) summarizes allocation scores (AS) across a range of possible values of the
constraint ($K$), allowing one to assign higher weights to more likely values of $K$ (Section
\ref{sec:methods.detailed.integrated_allocation}). 
IAS was computed for two weight distributions on the same grid of values of $K$ used in the sensitivity analysis above,
one uniform across the entire range and the other with weights proportional a truncated normal distribution centered at 15,000
(the orange and blue shaded areas in Figure
\ref{fig:multi-k}A, respectively).
With these weight distributions, the IAS defined in Equation~\eqref{eqn:IAS_definition} can be computed as the sum
$$S_{IAS}(F, y) = \sum_K S_A(F,y; K) p(K)$$

>>>>

The integrated allocation score (IAS) summarizes allocation scores (AS) across a range of possible values of the
constraint ($K$), allowing one to assign higher weights to more likely values of $K$ (Section
\ref{sec:methods.detailed.integrated_allocation}). 
IAS was computed for two weight distributions on the same grid of values of $K$ used in the sensitivity analysis above,
one uniform across the entire range and the other with weights proportional to a truncated normal distribution centered at 15,000
(the orange and blue shaded areas in Figure
\ref{fig:multi-k}A, respectively).
With these weight distributions, the IAS defined in Equation~\eqref{eqn:IAS_definition} can be computed as the sum
$$S_{IAS}(F, y) = \sum_K S_A(F,y; K) p(K)$$
